### 2025-02-09 data-visualization.qmd
20250208 - zoom in; don't remove data from plot

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point() +
  geom_smooth() +
  scale_x_continuous(
    expand = c(0,0), # set origin of x-axis to 0
    lim = c(20,40), # set limits of x-axis
    breaks = seq(from = 20, to = 40, by = 5) # specify x-axis labels
  ) +
  scale_y_continuous(
    expand = c(0,0), # set origin of y-axis to 0
    lim = c(0,NA), # set limits of y-axis
    breaks = seq(from = 0, to = 2500, by = 250) # specify y-axis labels
  )
```

@@

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point() +
  geom_smooth() +
  scale_x_continuous(
    expand = c(0,0),
    lim = c(20,40),
    breaks = seq(from = 20, to = 40, by = 5)
  ) +
  scale_y_continuous(
    expand = c(0,0),
    lim = c(0,NA),
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs( # add plot labels
    x = "Running Back's Age (years)",
    y = "Rushing Yards (Season)",
    title = "NFL Rushing Yards (Season) by Player Age",
    subtitle = "(Among Running Backs)"
  )
```

@@

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point() +
  geom_smooth() +
  scale_x_continuous(
    expand = c(0,0),
    lim = c(20,40),
    breaks = seq(from = 20, to = 40, by = 5)
  ) +
  scale_y_continuous(
    expand = c(0,0),
    lim = c(0,NA),
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs(
    x = "Running Back's Age (years)",
    y = "Rushing Yards (Season)",
    title = "NFL Rushing Yards (Season) by Player Age",
    subtitle = "(Among Running Backs)"
  ) +
  theme_classic() # use the classic theme
```

@@

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point() +
  geom_smooth() +
  scale_x_continuous(
    expand = c(0,0),
    lim = c(20,40),
    breaks = seq(from = 20, to = 40, by = 5)
  ) +
  scale_y_continuous(
    expand = c(0,0),
    lim = c(0,NA),
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs(
    x = "Running Back's Age (years)",
    y = "Rushing Yards (Season)",
    title = "NFL Rushing Yards (Season) by Player Age",
    subtitle = "(Among Running Backs)"
  ) +
  theme_dark() # use the dark theme
```

@@

plot_ypcByPlayerAge <- ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point(
    aes(
      text = player_display_name, # add player name for mouse over tooltip
      label = season)) + # add season for mouse over tooltip
  geom_smooth() +
  scale_x_continuous(
    expand = c(0,0),
    lim = c(20,40),
    breaks = seq(from = 20, to = 40, by = 5)
  ) +
  scale_y_continuous(
    expand = c(0,0),
    lim = c(0,NA),
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs(
    x = "Running Back's Age (years)",
    y = "Rushing Yards (Season)",
    title = "NFL Rushing Yards (Season) by Player Age",
    subtitle = "(Among Running Backs)"
  ) +
  theme_classic()

>>>>

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point() +
  geom_smooth() +
  coord_cartesian(
    xlim = c(20,40), # set limits of x-axis
    ylim = c(0,NA), # set limits of y-axis
    expand = FALSE) + # don't add space between axes and data
  scale_x_continuous(
    breaks = seq(from = 20, to = 40, by = 5) # specify x-axis labels
  ) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 2500, by = 250) # specify y-axis labels
  )
```

@@

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point() +
  geom_smooth() +
  coord_cartesian(
    xlim = c(20,40),
    ylim = c(0,NA),
    expand = FALSE) +
  scale_x_continuous(
    breaks = seq(from = 20, to = 40, by = 5) 
  ) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs( # add plot labels
    x = "Running Back's Age (years)",
    y = "Rushing Yards (Season)",
    title = "NFL Rushing Yards (Season) by Player Age",
    subtitle = "(Among Running Backs)"
  )
```

@@

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point() +
  geom_smooth() +
  coord_cartesian(
    xlim = c(20,40),
    ylim = c(0,NA),
    expand = FALSE) +
  scale_x_continuous(
    breaks = seq(from = 20, to = 40, by = 5) 
  ) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs(
    x = "Running Back's Age (years)",
    y = "Rushing Yards (Season)",
    title = "NFL Rushing Yards (Season) by Player Age",
    subtitle = "(Among Running Backs)"
  ) +
  theme_classic() # use the classic theme
```

@@

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point() +
  geom_smooth() +
  coord_cartesian(
    xlim = c(20,40),
    ylim = c(0,NA),
    expand = FALSE) +
  scale_x_continuous(
    breaks = seq(from = 20, to = 40, by = 5) 
  ) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs(
    x = "Running Back's Age (years)",
    y = "Rushing Yards (Season)",
    title = "NFL Rushing Yards (Season) by Player Age",
    subtitle = "(Among Running Backs)"
  ) +
  theme_dark() # use the dark theme
```

@@

plot_ypcByPlayerAge <- ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point(
    aes(
      text = player_display_name, # add player name for mouse over tooltip
      label = season)) + # add season for mouse over tooltip
  geom_smooth() +
  coord_cartesian(
    xlim = c(20,40),
    ylim = c(0,NA),
    expand = FALSE) +
  scale_x_continuous(
    breaks = seq(from = 20, to = 40, by = 5) 
  ) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs(
    x = "Running Back's Age (years)",
    y = "Rushing Yards (Season)",
    title = "NFL Rushing Yards (Season) by Player Age",
    subtitle = "(Among Running Backs)"
  ) +
  theme_classic()
